%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original Author:
% Debarghya Das (http://debarghyadas.com)
%
% Modified By:
% Achyudh Ram (http://achyudh.xyz)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{Achyudh_Resume}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}

\makeatletter
\renewcommand\@biblabel[1]{}
\renewenvironment{thebibliography}[1]
     {\section*{\refname}%
      \@mkboth{\MakeUppercase\refname}{\MakeUppercase\refname}%
      \list{}%
           {\leftmargin0pt
            \@openbib@code
            \usecounter{enumiv}}%
      \sloppy
      \clubpenalty4000
      \@clubpenalty \clubpenalty
      \widowpenalty4000%
      \sfcode`\.\@m}
     {\def\@noitemerr
       {\@latex@warning{Empty `thebibliography' environment}}%
      \endlist}
\makeatother
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{ACHYUDH}{RAM}{ \urlstyle{same}\href{http://achyudh.xyz}{http://achyudh.xyz} |
\href{mailto:arkeshav@uwaterloo.ca}{arkeshav@uwaterloo.ca} | \href{http://github.com/achyudh}{github.com/achyudh} | + 1 (226) 898 2242
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.32\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Languages}
Python \textbullet{} 
Java \textbullet{}
C\# \textbullet{} 
SQL \textbullet{} 
C \textbullet{} 
\LaTeX\ \\
\halfsectionsep

\subsection{Frameworks}
Hadoop \textbullet{}
Spark \textbullet{}
PyTorch \textbullet{} 
Keras \textbullet{} \\
Scikit-Learn \textbullet{}
Numpy \textbullet{}
NLTK \textbullet{}
Flask \\

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %     Projects
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\subsection{Tardis}
A framework for running ensembles of Seq2Seq Neural Machine Translation models on PySpark using Elephas \\

\subsection{Castor}
Deep learning models for computational linguistics in PyTorch by the Data Systems Group at the University of Waterloo \\ 

\subsection{Propr}
Developer feedback and report generation tools for improving the reviewability of pull requests on GitHub \\

\subsection{OpenEYE}
A web app to target misinformation on social issues by visualizing the dichotomy between facts and perceptions on Twitter \\

\subsection{Foresight}
An Android app that uses object detection, Google Places API, and Firebase to help the differently-abled navigate better \\

% \subsection{DevCAP}
% An analysis framework to decode the social structure of developer mailing lists, IRC and Slack channels \\

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %     Coursework
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Coursework}
% \subsection{Graduate}
% Introduction to Machine Learning \\
% Neural Networks \& Fuzzy Logic \\
% Data-Intensive Distributed Computing \\
% Advanced Topics in AI \\
% Empirical Software Evolution \\
% Advanced Topics in Software Engg. \\
% \halfsectionsep
% \subsection{Undergraduate}
% Information Retrieval \\
% Parallel Computing \\
% Data Structures \& Algorithms \\
% Design \& Analysis of Algorithms \\
% Computer Architecture \\
% Discrete Structures\\
% Computer Networks \\
% Compiler Construction \\
% Operating Systems \\
% Logic in Computer Science \\
% Theory of Computation \\
% Principles of Programming Languages \\
% Object Oriented Programming \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Talks
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Talks}
\subsection{Google Developer Group}
\location{Apr 2017 | Goa, India}
Leveraging the power of Virtualization, Docker and the Cloud \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Teaching
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Teaching} 
% Introduction to Computer Science \\
% Designing Functional Programs \\
% Data Structures \& Algorithms \\
% Neural Networks \& Fuzzy Logic \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.655\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{Microsoft Research}
\descript{| Software Engineering Intern }
\location{May 2018 - Aug 2018 | Bangalore, India}
Worked on query optimization for COSMOS, Microsoft's production Big Data engine, by developing static analysis tools for queries written in SCOPE, a SQL-like declarative language
\sectionsep

\runsubsection{Intuit}
\descript{| Software Engineering Intern }
\location{May 2017 – Jul 2017 | Bangalore, India}
Developed a data processing engine with parallel query evaluation for layout-based database retrieval and a report generation layer that provides performance insights for businesses 300\% faster than an existing internal solution
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Research}
\runsubsection{University of Waterloo}
\descript{| Graduate Research Assistant}
\location{Aug 2018 – Present | Waterloo, Canada}
Worked with Prof. Jimmy Lin from the \textbf{Data Systems Group} on building deep learning models for natural language processing tasks
\sectionsep

\runsubsection{University of Waterloo}
\descript{| Research Intern}
\location{Jan 2018 – May 2018 | Waterloo, Canada}
Worked with the \textbf{Software Analytics Group} and the \textbf{Computational Health Informatics Lab} on hierarchical deep learning models for supervised sentiment analysis on software datasets
\sectionsep

\runsubsection{Delft University of Technology}
\descript{| Research Intern}
\location{Aug 2017 – Dec 2017 | Delft, Netherlands}
Worked with the \textbf{Software Engineering Research Group} on assessing the reviewability and automating the quality evaluation of pull requests
\sectionsep

\runsubsection{Indian Bank}
\descript{| Research Intern}
\location{May 2015 – Jul 2015 | Chennai, India}
Developed environment sensitive time-series forecasting models for setting business targets for the \textbf{Planning and Economic Research Division}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\runsubsection{University of Waterloo}
\descript{| Ontario, Canada}
\vspace{\topsep}
\begin{tightemize}
\item[]\locationbf{M.Math. (Thesis) Computer Science}
Cumulative GPA: 4.0 / 4.0
\end{tightemize}

\sectionsep

\runsubsection{Birla Institute of Technology and Science}
\descript{| Pilani, India}
\begin{tightemize}
\item[] \locationbf{B.E. (Honors) in Computer Science, Aug 2018}
Cumulative GPA: 3.88 / 4.0 | Major GPA: 3.89 / 4.0
\halfsectionsep
\item[] \locationbf{M.Sc. (Honors) in Economics, Aug 2018}
Major GPA: 4.0 / 4.0
\end{tightemize}
\end{minipage} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PUBLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Publications}
\begin{itemize}
    \item[] What Makes a Code Change Easier to Review? An Empirical Investigation on Code Change Reviewability. In \textit{Proceedings of the 26th ACM Joint European Software Engineering Conference and Symposium on the Foundations of Software Engineering.} 2018.
    \item[] Investigating Type Declaration Mismatches in Python. In \textit{IEEE Workshop on Machine Learning Techniques for Software Quality Evaluation.} 2018.
    \item[] Supervised Sentiment Classification with CNNs for Diverse SE Datasets. \textit{arXiv preprint arXiv:1812.09653.} 2019.
\end{itemize}

% \renewcommand\refname{\vskip -1.5em}
% \bibliographystyle{abbrv}
% \bibliography{Achyudh_Resume}
% \nocite{*}
\end{document}  
